### 2017-09-20 monograph/thesis/chapters/implementação.tex
Renamed newtcolorbox from myquote to bluebox

    \medskip
    \begin{myquote}
    ``As formas que o código é exibido ao usuário e que ele é salvo em disco são controladas
    por arquivos de configuração distintos. O arquivo ``theme.ini'' contém, entre outras
    configurações, informações de como serializar a árvore sintática.''
    \end{myquote}

    \vspace{-5mm}
    ...
    \begin{myquote}
    ``A configuração de formato de saída é dada da mesma forma, mas em um arquivo
    separado, chamado ``output\_format.ini''. A decisão desta separação foi em vista de equipes
    de programadores que queiram utilizar uma convenção única para os arquivos salvos,
    mas manter a exibição a escolha de cada um. Assim os integrantes desta equipe podem
    compartilhar os seus arquivos ``output\_format.ini'' enquanto personalizam o arquivo
    ``theme.ini'' a seu gosto.''
    \end{myquote}

@@

    \medskip
    \begin{myquote}
    \begin{enumerate}[nolistsep]
        \item Criar um formatador de fácil configuração e expansão para as linguagens de
              programação que existem e que irão existir.
    \end{enumerate}
    \end{myquote}

@@

    \medskip
    \begin{myquote}
    \begin{enumerate}[nolistsep]
        \item Add new lines after ``\{'' and before ``\}''
        \item Add new lines before ``\{''
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after ``;''
        \item Add new lines after ``\}''
        \item Remove new lines
        \item Reduce whitespace
        \item Put the code again in the input box above after submit
    \end{enumerate}
    \end{myquote}

@@

        \begin{myquote}
        % \setlength{\itemindent}{5pt}
        ``One of absolute worst, worst methods of teamicide for software developers is to engage
        in these kinds of passive-aggressive formatting wars. I know because I've been there.
        They destroy peer relationships, and depending on the type of formatting, can also damage
        your ability to effectively compare revisions in source control, which is really scary.
        I can't even imagine how bad it would get if the lead was guilty of this behavior. That's
        leading by example, all right. Bad example.'', \cite{Atwood}.
        \end{myquote}
        \vspace{-5mm}
        ...
        \begin{myquote}
        ``So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
        trivial issues of code layout is actually justified. Within reason of course -- when done
        openly, in a fair and concensus building way, and without stabbing your teammates in the
        face along the way.'', \cite{Atwood}.
        \end{myquote}

        \begin{myquote}``
        I'd say there are two main reasons to enforce a single code format in a project. First has
        to do with version control: with everybody formatting the code identically, all changes in
        the files are guaranteed to be meaningful. No more just adding or removing a space here or
        there, let alone reformatting an entire file as a `side effect' of actually changing just a
        line or two.'', \cite{Geukens}.
        \end{myquote}

@@

    \medskip
    \begin{myquote}
    \begin{enumerate}[leftmargin=*]

@@

    \end{enumerate}
    \end{myquote}

@@

    \begin{myquote}
    \begin{enumerate}[leftmargin=*,parsep=0pt]

@@

    \medskip
    \begin{sloppypar}
    \begin{myquote}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

@@

    \end{enumerate}
    \end{myquote}
    \end{sloppypar}

@@

    % How to add `parsep` to `itemsep` and set `parsep` to 0pt, when declaring my list?
    % https://tex.stackexchange.com/questions/366904/how-to-add-parsep-to-itemsep-and-set-parsep-to-0pt-when-declaring-my-list
    \begin{sloppypar}
    \begin{myquote}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

@@

    \begin{sloppypar}
    \begin{myquote}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

>>>>

    \medskip
    \begin{bluebox}
    ``As formas que o código é exibido ao usuário e que ele é salvo em disco são controladas
    por arquivos de configuração distintos. O arquivo ``theme.ini'' contém, entre outras
    configurações, informações de como serializar a árvore sintática.''
    \end{bluebox}

    \vspace{-5mm}
    ...
    \begin{bluebox}
    ``A configuração de formato de saída é dada da mesma forma, mas em um arquivo
    separado, chamado ``output\_format.ini''. A decisão desta separação foi em vista de equipes
    de programadores que queiram utilizar uma convenção única para os arquivos salvos,
    mas manter a exibição a escolha de cada um. Assim os integrantes desta equipe podem
    compartilhar os seus arquivos ``output\_format.ini'' enquanto personalizam o arquivo
    ``theme.ini'' a seu gosto.''
    \end{bluebox}

@@

    \medskip
    \begin{bluebox}
    \begin{enumerate}[nolistsep]
        \item Criar um formatador de fácil configuração e expansão para as linguagens de
              programação que existem e que irão existir.
    \end{enumerate}
    \end{bluebox}

@@

    \medskip
    \begin{bluebox}
    \begin{enumerate}[nolistsep]
        \item Add new lines after ``\{'' and before ``\}''
        \item Add new lines before ``\{''
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after ``;''
        \item Add new lines after ``\}''
        \item Remove new lines
        \item Reduce whitespace
        \item Put the code again in the input box above after submit
    \end{enumerate}
    \end{bluebox}

@@

        \begin{bluebox}
        % \setlength{\itemindent}{5pt}
        ``One of absolute worst, worst methods of teamicide for software developers is to engage
        in these kinds of passive-aggressive formatting wars. I know because I've been there.
        They destroy peer relationships, and depending on the type of formatting, can also damage
        your ability to effectively compare revisions in source control, which is really scary.
        I can't even imagine how bad it would get if the lead was guilty of this behavior. That's
        leading by example, all right. Bad example.'', \cite{Atwood}.
        \end{bluebox}
        \vspace{-5mm}
        ...
        \begin{bluebox}
        ``So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
        trivial issues of code layout is actually justified. Within reason of course -- when done
        openly, in a fair and concensus building way, and without stabbing your teammates in the
        face along the way.'', \cite{Atwood}.
        \end{bluebox}

        \begin{bluebox}``
        I'd say there are two main reasons to enforce a single code format in a project. First has
        to do with version control: with everybody formatting the code identically, all changes in
        the files are guaranteed to be meaningful. No more just adding or removing a space here or
        there, let alone reformatting an entire file as a `side effect' of actually changing just a
        line or two.'', \cite{Geukens}.
        \end{bluebox}

@@

    \medskip
    \begin{bluebox}
    \begin{enumerate}[leftmargin=*]

@@

    \end{enumerate}
    \end{bluebox}

@@

    \begin{bluebox}
    \begin{enumerate}[leftmargin=*,parsep=0pt]

@@

    \medskip
    \begin{sloppypar}
    \begin{bluebox}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

@@

    \end{enumerate}
    \end{bluebox}
    \end{sloppypar}

@@

    % How to add `parsep` to `itemsep` and set `parsep` to 0pt, when declaring my list?
    % https://tex.stackexchange.com/questions/366904/how-to-add-parsep-to-itemsep-and-set-parsep-to-0pt-when-declaring-my-list
    \begin{sloppypar}
    \begin{bluebox}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

@@

    \begin{sloppypar}
    \begin{bluebox}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]
